### 2014-01-27 brains-protocol.tex
Rephrasing in 3.1 dataset

We thus relied on a large and reliable quotation dataset collected by \citet{Leskovec09} which 
%matched these essential criteria: made of public representations, subject to variations which could be expected to be of a relatively moderate magnitude, be ideally described by reference to an ideal original representation, and 
is of a sufficiently large size to lend itself to statistical analysis.
%\tb{On a donc choisi de s'appuyer sur un corpus déjà disponible au lieu de construire le nôtre, ce qui est une des raisons pour lesquelles l'analyse de la question est si tributaire du choix des données.  Le jeu de données utilisé par  et \citet{Simmons11} se prête bien à la notion de représentation publique qu'on a choisie ci-dessus. Construit et publié en 2009 par \citeauthor{Leskovec09}, c'est un jeu de données reconnu et utilisé dans la littérature, largement pré-traité pour nos besoins comme on le verra ci-dessous. Il est d'une dimension bien suffisante pour atteindre des niveaux de significativité intéressants, tout en restant manipulable sur un serveur de calcul modeste ou même sur un bon ordinateur portable.}
This dataset consists of the daily collection of news stories or blog posts from around a million online sources, with the approximate publication rate of 900k texts per day, over a nine-month period ranging from August 2008 to April 2009 \cite{Leskovec09-url}.\footnote{The original article~\citep{Leskovec09} does not provide additional details on the method of source selection.}
Quotations were then automatically extracted from this corpus: each quotation is a more or less faithful excerpt of an utterance (oral or written) by the cited person. Quotations were then gathered in a graph and connected according to their similarity: either because they differ by very few words (in that case, no more than one word) or because they share a certain sequence of words (in that case, at least ten consecutive words). A community detection algorithm is applied to that quotation graph to detect aggregates of tightly connected, i.e. sufficiently similar, groups of quotations (see \citet{Leskovec09} for more detail).  The final data contains around $70,000$ sets of quotations. Each set allegedly contains all variations of a same parent utterance, annotated with the respective URLs and timestamps of publication of each individual variation. % We have the list of occurrences, URL and publication time of the quotations of a given such set. %  which are possibly slightly differing from a parent utterance.

%\tb{Un des travaux des auteurs a été de reconstituer ces ensembles de citations par une méthode de catégorisation (i.e. construction de \emph{clusters})\footnote{Se référer à \citet{Leskovec09} pour plus de détails. Ce traitement des données comporte aussi quelques étapes de filtrage, décrites dans l'article.}, et c'est à ce stade de traitement qu'on obtient les données : elles sont constituées d'environs 70~000 ensembles de citations, à l'intérieur desquels toutes les citations proviennent d'un même énoncé parent (elles en sont des sous-parties transformées). Pour chaque citation à l'intérieur de chaque ensemble, on a une liste de triplets \emph{(URL, date d'apparition, nombre d'occur\-rences à cette URL)} décrivant les adresses et les dates auxquelles cette citation est apparue.}

>>>>

We relied on a reliable quotation dataset collected by \citet{Leskovec09}, large enough to lend itself to statistical analysis.
This dataset consists of the daily crawling of news stories and blog posts from around a million online sources, with an approximate publication rate of 900k texts per day, over a nine-month period of time (from August 2008 to April 2009) \cite{Leskovec09-url}.\footnote{Unfortunately, the original article~\citep{Leskovec09} does not provide additional details on the source selection methodology.}
Quotations were then automatically extracted from this corpus: each quotation is a more or less faithful excerpt of an utterance (oral or written) by the quoted person.
Quotations were then gathered in a graph and connected according to their similarity: either because they differ by very few words (in that case, no more than one word) or because they share a certain sequence of words (in that case, at least ten consecutive words).
A community detection algorithm was applied to that quotation graph to detect aggregates of tightly connected, i.e. sufficiently similar, groups of quotations (see \citet{Leskovec09} for more detail).
This analysis yielded the final data, with a total of about $70,000$ sets of quotations; each of these sets allegedly contains all variations of a same parent utterance, annotated with the respective publication URLs and timestamps of each individual variation.
